**Differences in COVID-19 vaccination in the province of Ontario across Health Regions and socio-economic strata**

### 2023-04-16 manuscript_v3/appendix.tex
Updated months, fix descriptive table as September still appears

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, interior hidden, sharp corners, boxrule=0pt, breakable, enhanced, frame hidden]}{\end{tcolorbox}}\fi

@@

We used the iterative proportional fitting procedure (\emph{raking}) in
order to account for the differences in income, age groups,
race/ethnicity and the population from the Health Regions. Details of
the implementation can be found in the R Script
\texttt{raking\_logistic\_regression.R} in the \texttt{code} directory.

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, interior hidden, frame hidden, breakable, sharp corners, boxrule=0pt, enhanced]}{\end{tcolorbox}}\fi

@@

We used the iterative proportional fitting procedure (\emph{raking}) in
order to account for the differences in income, age groups,
race/ethnicity and the population from the Health Regions. Details of
the implementation can be found in the R Script \texttt{raking.R} in the
\texttt{code} directory.

### 2023-04-16 manuscript_v3/main.qmd
Updated months, fix descriptive table as September still appears

---
title: '**COVID-19 vaccination in Ontario: Exploring intra-provincial variations within Health Regions and socio-economic strata**'
authors:
  - name: Ariel Mundo Ortiz
    affiliations:
      - ref: crm
    email: ariel.mundo.ortiz@umontreal.ca
    orcid: 0000-0002-6014-4538
  - name: Bouchra Nasri
    affiliations:
      - ref: espum
    email: bouchra.nasri@umontreal.ca
    corresponding: true
affiliations:
  - id: crm
    name: Centre de Recherches Mathématiques, University of Montreal, Montréal, Canada
  - id: espum
    name: Department of Social and Preventive Medicine, École de Santé Publique, University of Montreal, Montréal, Canada 
filters:
  - authors-block
format: 
  pdf:
    include-in-header: latex/preamble.sty
    #mainfont: "Palatino Linotype"
    keep-tex: true
#linestretch: 1
bibliography: references/refs.bib
csl: references/jama.csl
link-citations: yes #adds links to the citations
---

>>>>

---
title: '**Differences in COVID-19 vaccination in the province of Ontario across Health Regions and socio-economic strata**'
authors:
  - name: Ariel Mundo Ortiz
    affiliations:
      - ref: crm
      - ref: espum
    email: ariel.mundo.ortiz@umontreal.ca
    orcid: 0000-0002-6014-4538
  - name: Bouchra Nasri
    affiliations:
      - ref: crm
      - ref: espum
    email: bouchra.nasri@umontreal.ca
    corresponding: true
affiliations:
  - id: crm
    name: Centre de Recherches Mathématiques, University of Montreal, Montréal, Canada
  - id: espum
    name: Department of Social and Preventive Medicine, École de Santé Publique, University of Montreal, Montréal, Canada 
filters:
  - authors-block
format: 
  pdf:
    include-in-header: latex/preamble.sty
    #mainfont: "Palatino Linotype"
    keep-tex: true
#linestretch: 1
bibliography: references/refs.bib
csl: references/jama.csl
link-citations: yes #adds links to the citations
---
